---
title: "Generate Figures"
author: "Zach"
date: 2018-05-19
output: 
  github_document:
    toc: true
---

## Setup and Wrangling
<!-- ----------------------------------------------------------------------- -->

```{r setup, include=FALSE}
# knitr options
knitr::opts_chunk$set(echo = FALSE)
```

```{r settings, echo=FALSE}
library(tidyverse)

## Parameters: Data ------------------------------------------------------------
# Extension
ext <- "eps"
asp_ratio <- 3 / 4
img_width <- 5
img_height <- img_width * asp_ratio

# Data directory
dir_data <- "~/Git/mat-stat-uq/data"
# Find all the data files
files_all <- 
  tibble(
    files = list.files(dir_data, full.names = TRUE)
  ) %>% 
  mutate(
    name = str_sub(str_extract(files, "[^/]+\\."), 1, -2)
  )

# Beam directory
dir_beam      <- "~/Git/mat-stat-uq/code/beam/results/"
file_beam_out <- "out.txt"
subdir_beam   <- c("bv/", "md_ldm/", "mip_ldm/", "pi/")
subdir_method <- c("bv/" = "bv", "md_ldm/" = "mil", "mip_ldm/" = "mip", "pi/" = "pi")
# subdir_beam   <- c("bv/", "md_ldm/", "mip_ldm/")
# subdir_method <- c("bv/" = "bv", "md_ldm/" = "mil", "mip_ldm/" = "mip")

beam_rel     <- 1 - 0.00135 # Desired reliability in optimization problem
beam_con     <- 0.95        # Desired confidence level
beam_pop     <- 0.99        # Desired population fraction
beam_entries <- 10          # Number of entries (lines) per case in a result file
beam_samp    <- 40          # Number of replications for statistics
# beam_samp    <- 1         # Number of replications for statistics

zc_one <- qnorm(beam_con)
zc_two <- -qnorm((1 - beam_con) / 2)

## Parameters: Aesthetics ------------------------------------------------------

# Named color palette
cbPalette <- c(
  "bv"  = "#000000", 
  "pi"  = "#E69F00", 
  
  "mil" = "#56B4E9", 
  "mil2" = "#F0E442", 
  "mil3" = "#0072B2", 
  "mil4" = "#009E73", 
  "mil5" = "#F0E442", 
  
  "mip" = "#009E73", 
  "mip3" = "#F0E442", 
  "mip4" = "#0072B2", 
  "mip5" = "#D55E00", 
  
  "pri" = "#CC79A7",
  "pri3" = "#CC79A7",
  "pri4" = "#CC79A7",
  "pri5" = "#CC79A7"
)
# Named labels
colLabels <- c(
  "bv"  = "A-basis value",
  "pi"  = "Plug-in",
  "mil" = "MIL",
  "mil2" = "MIL; L = 100",
  "mil3" = "MIL; L = 1,000",
  "mil4" = "MIL; L = 10,000",
  "mil5" = "MIL; L = 100,000",
  
  "mip" = "MIP",
  "mip3" = "MIP; L = 1,000",
  "mip4" = "MIP; L = 10,000",
  "mip5" = "MIP; L = 100,000",
  
  "pri" = "PRI",
  "pri3" = "PRI; L = 1,000",
  "pri4" = "PRI; L = 10,000",
  "pri5" = "PRI; L = 100,000"
)

## Helper functions ------------------------------------------------------------
base_breaks <- function(n = 10){
    function(x) {
        axisTicks(log10(range(x, na.rm = TRUE)), log = TRUE, n = n)
    }
}
```

Let's check which files were found.

```{r check_files}
files_all
```

Load and wrangle all the files in `/data/`.

```{r load_and_wrangle, echo=FALSE}
# Define load function for map()
load_fcn <- function(filename) {
  # Read and wrangle
  df_base <- 
    read_csv(filename) %>% 
    select(N, C, P, R, everything()) %>% 
    select(-X1) %>% 
    gather(key = "idet", value = "value", matches("^[M|R]_")) %>% 
    separate(idet, into = c("type", "method", "stat"), sep = "_") %>% 
    spread(key = stat, value = value)
  
  # Compute failure probabilities
  df_fail <- 
    df_base %>% 
    filter(type == "R") %>% 
    mutate(
      type = "F",
      hi = 1 - hi,
      lo = 1 - lo,
      mu = 1 - mu
    )
  
  # Bind and keep the name
  df_base %>% 
    bind_rows(df_fail) %>% 
    structure(name = str_extract(filename, "[^/]+\\."))
}

# Load all the files to a master tibble
list_df <- 
  tibble(
    data = map(files_all$files, load_fcn),
    name = files_all$name
  )
```

Next, let's load the beam result files. These are in a different format, and have more than one reliability constraint; thus we'll need to treat them differently.

```{r}
# Define loading function
load_beam <- function(subdir) {
  # Load the files
  df_res <- 
    str_c(dir_beam, subdir, file_beam_out) %>% 
    read_delim(
      delim = ":",
      col_names = c(
        "type",
        "value"
      ),
      col_types = cols(
        type = col_character(),
        value = col_number()
      )
    )
  
  # Remove the exact solution from the top
  objective_exact <- df_res %>% slice(1) %>% pull(value)
  
  df_res <- 
    df_res %>% 
    slice(-1) %>% 
    mutate(
      type = str_replace_all(type, "[:punct:]", ""),
      type = tolower(str_replace_all(type, "\\s+", "_"))
    )
  
  # Define helper functions and compute parameters
  total <- dim(df_res)[1]
  wid <- as.integer(total / beam_entries)
  slc <- c(0:(wid - 1))
  
  make_row <- function(idx) {
    df_res %>% 
      slice((idx * beam_entries + 1):((idx+1) * beam_entries)) %>% 
      spread(key = type, value = value)
  }
  
  # `spread()` to get one `sample_count` per row
  df_res <- 
    map_dfr(slc, make_row) 
    
  # Mutate to compute statistics
  # Note that the `sd` terms in the data are actually standard errors...
  df_res <-
    df_res %>%
    mutate(
      R = beam_rel,
      C = beam_con,
      P = beam_pop,
      method = subdir_method[[subdir]],
      
      M_mu = (objective_mean - objective_exact) / objective_exact,
      M_lo = (objective_mean - zc_one * objective_sd - objective_exact) / objective_exact,
      M_hi = (objective_mean + zc_one * objective_sd - objective_exact) / objective_exact,
      
      R_d_mu = reliability_disp_mean,
      R_d_lo = reliability_disp_mean - zc_one * reliability_disp_sd,
      R_d_hi = reliability_disp_mean + zc_one * reliability_disp_sd,
      
      R_s_mu = reliability_stress_mean,
      R_s_lo = reliability_stress_mean - zc_one * reliability_stress_sd,
      R_s_hi = reliability_stress_mean + zc_one * reliability_stress_sd,
      
      F_d_mu = 1 - R_d_mu,
      F_d_lo = 1 - R_d_lo,
      F_d_hi = 1 - R_d_hi,
      
      F_s_mu = 1 - R_s_mu,
      F_s_lo = 1 - R_s_lo,
      F_s_hi = 1 - R_s_hi
    ) 
  
  # Gather, code, then spread
  df_res <- 
    df_res %>% 
    rename(N = sample_count) %>% 
    select_if(!str_detect(names(.), "(objective|reliability)")) %>% 
    gather(key = "idet", value = "value", M_mu:F_s_hi) %>% 
    extract(idet, into = c("type", "stat"), regex = "^(.+)_(\\w+)$") %>% 
    spread(key = stat, value = value)
}

## Load all
df_beam <- 
  map_dfr(subdir_beam, load_beam) %>% 
  glimpse()
```


## Figure Aesthetics
<!-- ----------------------------------------------------------------------- -->
Here we define the figure specifications.

```{r}
# Common theme settings
theme_common <- function() {
  theme_minimal() %+replace%
  theme(
    axis.text.x = element_text(size = 12),
    axis.text.y = element_text(size = 12),
    axis.title.x = element_text(margin = margin(4, 4, 4, 4), size = 16),
    axis.title.y = element_text(margin = margin(4, 4, 4, 4), size = 16, angle = 90),
    
    aspect.ratio = 3 / 4,
    
    plot.margin   = unit(c(t = +0, b = +0, r = +0, l = +0), "cm"),
    panel.spacing = unit(c(t = +0, b = +0, r = +0, l = +0), "cm"),
    
    legend.text = element_text(size = 10),
    
    panel.grid.major = element_line(color = "grey90"),
    panel.grid.minor = element_line(color = "grey90")
  )
}

# Baseline margin plot
margin_plot <- function(df) {
  df_sort <- 
    df %>% 
    filter(N == max(N), type == "M") %>% 
    select(N, method, lo) %>% 
    arrange(desc(lo))
  
  df %>% 
    filter(str_detect(type, "M")) %>% 
    mutate(method = fct_relevel(method, df_sort$method)) %>% 
    ggplot(aes(x = N, color = method)) +
    geom_hline(
      aes(yintercept = 0, linetype = "Requested"),
      size = 1
    ) +
    geom_line(aes(y = mu, linetype = "Mean") ) + 
    scale_y_continuous(
      labels = scales::percent
    ) +
    scale_x_log10(
      labels = scales::trans_format("log10", scales::math_format(10^.x))
    ) +
    scale_color_manual(
      name = "Method",
      values = cbPalette,
      labels = colLabels
    ) +
    scale_linetype_manual(
      name = "Type",
      values = c("Requested" = 2, "Mean" = 1, "CI" = 3)
    ) +
    theme_common() +
    labs(
      x = "Sample Count (m)",
      y = "Effective Margin"
    )
}

# Baseline margin plot
failure_plot <- function(df) {
  R_target <- min(df$R)
  
  df_sort <- 
    df %>% 
    filter(N == max(N), str_detect(type, "F")) %>% 
    select(N, method, lo) %>% 
    arrange(desc(lo))
  
  df %>% 
    filter(str_detect(type, "F")) %>% 
    mutate(method = fct_relevel(method, df_sort$method)) %>% 
    ggplot(aes(x = N, color = method)) +
    geom_hline(
      aes(yintercept = 1 - R_target, linetype = "Requested"),
      size = 1
    ) +
    geom_line(aes(y = mu, linetype = "Mean")) + 
    scale_y_log10(
      breaks = 10 ^ (-14:0),
      labels = scales::trans_format("log10", scales::math_format(10^.x))
    ) +
    scale_x_log10(
      labels = scales::trans_format("log10", scales::math_format(10^.x))
    ) +
    scale_color_manual(
      name = "Method",
      values = cbPalette,
      labels = colLabels
    ) +
    scale_linetype_manual(
      name = "Type",
      values = c("Requested" = 2, "Mean" = 1, "CI" = 3)
    ) +
    theme_common() +
    labs(
      x = "Sample Count (m)",
      y = "Effective Failure Chance"
    )
}

# Add two-sided CI
ci_two <- function(plt) {
  plt +
  geom_ribbon(
    aes(ymin = lo, ymax = hi, color = method, group = method, linetype = "CI"), 
    alpha = 1 / 5, 
    fill = "grey80"
  )
}

# Add one-sided CI
ci_one <- function(plt) {
  plt +
  geom_ribbon(
    aes(ymin = lo, ymax = mu, color = method, group = method, linetype = "CI"), 
    alpha = 1 / 5, 
    fill = "grey80"
  )
}

# Test the figures
name_sel <- "an_mil_c0"

df_sel <- 
  list_df %>% 
  filter(name == name_sel) %>% 
  .$data

df_sel[[1]] %>% 
  margin_plot() %>%
  ci_one()

df_sel[[1]] %>%
  failure_plot() %>%
  ci_one()
```

## Figure Generation
<!-- ----------------------------------------------------------------------- -->

We can handle most of the figures using the same call. We first filter out the 'special' cases, and run the remaining ones.

```{r}
# Get all the common (simple) files
list_common <- 
  list_df %>% 
  filter(!str_detect(name, "an_tension")) %>% 
  filter(!str_detect(name, "mc_mip"))

# Define what to do with them
gen_margin_common <- function(df) {
  df %>% 
    margin_plot() %>% 
    ci_one() %>% 
    
  ggsave(filename = str_c("../../images/M_", attr(df, "name"), ext), height = img_height, width = img_width, units = "in")
}

gen_failure_common <- function(df) {
  df %>% 
    failure_plot() %>% 
    ci_one() %>% 
    
  ggsave(filename = str_c("../../images/F_", attr(df, "name"), ext), height = img_height, width = img_width, units = "in")
}

# Start the reactor!
walk(.f = gen_margin_common, .x = list_common$data)
walk(.f = gen_failure_common, .x = list_common$data)
```

The MIP results use the same functions, but contain more results than we'd like to plot. Filter, do some re-naming, and generate figures.

```{r}
# Remove the PRI results; convergence study
df_mip1 <- 
  list_df %>% 
  filter(name == "mc_mip_c0_balance") %>% 
  .$data %>% 
  .[[1]] %>% 
  filter(!str_detect(method, "pri"))

# Focus on high-simulation results
df_mip2 <- 
  list_df %>% 
  filter(name == "mc_mip_c0") %>% 
  .$data %>% 
  .[[1]] %>% 
  filter(method %in% c("mip5", "pri5"))

# Generate MIP figures
gen_margin_common(df_mip1)
gen_margin_common(df_mip2)

gen_failure_common(df_mip1)
gen_failure_common(df_mip2)
```

The analytical tension cases use a two-sided CI; let's handle those.

```{r}
# Grab the analytical tension cases
list_ten <- 
  list_df %>% 
  filter(str_detect(name, "an_tension"))

# Define what to do with them
gen_margin_ten <- function(df) {
  df %>% 
    margin_plot() %>% 
    ci_two() %>% 
    
  ggsave(filename = str_c("../../images/M_", attr(df, "name"), ext), height = img_height, width = img_width, units = "in")
}

gen_failure_ten <- function(df) {
  df %>% 
    failure_plot() %>% 
    ci_two() %>% 
    
  ggsave(filename = str_c("../../images/F_", attr(df, "name"), ext), height = img_height, width = img_width, units = "in")
}

# Generate the figures
walk(.f = gen_margin_ten, .x = list_ten$data)
walk(.f = gen_failure_ten, .x = list_ten$data)
```

Finally, let's process the cantilever beam results. These are in a still-different format, but there's really only one case, so we can do them manually.

```{r}
# First, the effective margin results only
df_beam %>% 
  filter(type == "M") %>% 
  margin_plot() %>% 
  ci_one()
ggsave(filename = str_c("../../images/M_beam.", ext), height = img_height, width = img_width, units = "in")

# Next, the two reliability plots
df_beam %>% 
  filter(type == "F_d") %>% 
  failure_plot() %>% 
  ci_one()
ggsave(filename = str_c("../../images/F_beam_disp.", ext), height = img_height, width = img_width, units = "in")

df_beam %>% 
  filter(type == "F_s") %>% 
  failure_plot() %>% 
  ci_one()
ggsave(filename = str_c("../../images/F_beam_stress.", ext), height = img_height, width = img_width, units = "in")
```

